---
title: "Lab 6"
author: "Devon Rossi"
date: "11/2/2021"
output: html_document
---
#Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Attach packages (adding broom and equatiomatic)

library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Rank based test 

Mann-Whitney U (non-parametric alternative to an unpaired 2-sample t-test).

H0: Equal ranks (or medians) - samples are drawn from pops w/ equal ranks or median values
HA: Ranks are not equal (or, medians are not equal)

### Create samples

`set.seed()` to create "pseudorandom, but reproducible samples"

```{r}
set.seed(1414) #run set.seed first
gp_1 <- sample.int(20, size = 15, replace = TRUE) #group 1, sample, 1-20, replacement = TRUE 

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE) #group 2, sample, 1-30, replacement = TRUE
```

Take a quick look at the distributions using the `hist()`.

```{r}
hist(gp_1) #not convincingly normally distributed
hist(gp_2) 
```

Try a t-test so we can compare the results:

```{r}
ttest <- t.test(gp_1, gp_2)

#If these data were paired, I can just add the argument 'paired  = "TRUE"' within the t.test() function.
```

This p-value means that IF our samples are drawn from populations with the same mean (i.e., if they null hypothesis is true), there is `r round(ttest$p.value,2)` probably of finding sample means *at least as different* as mine by random chance.


I don't think that my samples are so different that I think I have enough evidence to reject the null that they're from populations with the same mean.